\documentclass[10pt]{article}
    \usepackage[english]{babel}
    \input{config/minimal-resume-config}
    \begin{document}
    
\begin{center}
	% Personal
	% -----------------------------------------------------
	{\fontsize{\sizeone}{\sizeone}\fontspec[Path = fonts/,LetterSpace=15]{Montserrat-Regular} ZOE E GAGNON}
	\\
	\vspace{2mm}
	{\fontsize{1em}{1em}\fontspec[Path = fonts/]{Montserrat-Light} zoe@zgagnon.com -- 7203014407 -- Beacon NY -- zgagnon.com}
\end{center}

% Chapter: Work Experience
% ------------------------
\chap{EXPERIENCE}{
	
	\job
	{Orgspace}
	{Oct 2021 – Present}
	{Principle Engineer}
	{Beacon NY}
	{
	\begin{newitemize}
		\item {Principal engineer for seed series startup. Responsible for all technical direction.}
		\item {Owned vendor relationships, from selection to implementation.}
		\item {Instrumental in company strategy, introduced frameworks to analyze potential customer tranches, assess needs, and identify product opportunities.}
	\end{newitemize}
		}

	\job
	{Parachute Health}
	{Jun 2020 - Oct 2021}
	{Software Engineering Manager}
	{Beacon NY}
	{
	\begin{newitemize}
		\item {	First engineering manager in the company, with a team of eight engineers. Es-
		tablished all processes for leveling, coaching, and performance management.}
		\item {With CTO, planned growth strategy. Developed sourcing plan, interviews, and hiring process.}
		\item {Identified strategic needs and created software solutions, company-wide.}
	\end{newitemize}
	}

	\job
	{Meetup}
	{Aug 2018 - Mar 2020}
	{Software Engineering Manager}
	{New York, NY}
	{
	\begin{newitemize}
		\item Manager and Technical Lead for a team of six software engineer and software
		engineer in test personnel.
		\item Leader in technical and process strategy across the company, introducing several
		new technical innovations and improving work streams.
		\item Management consultant to other managers. Led working groups to formalize leveling and
		career development across the engineering organization.
	\end{newitemize}
	}

	\job
	{Pivotal Labs}
	{Dec 2017 - Aug 2018}
	{Software Engineering Manager}
	{New York, NY}
	{
	\begin{newitemize}
		\item Coached two software engineers in advancing their careers.
		\item Advanced agile and engineering practices both within and without the company.
		\item Developed innovative practices for cloud and micro-services based React front end applications.
	\end{newitemize}
	}

	\job
	{Pivotal Labs}
	{Oct 2015 - Dec 2017}
	{Senior Software Engineer}
	{New York, NY}
	{
	\begin{newitemize}
		\item Led balanced product development teams and multi-team efforts to deliver high impact software for
		Fortune 100 clients.
		\item Enabled developers and stakeholders in evidence-driven, value-first agile software development.
		\item Designed and implemented sustainable cloud based applications and platforms.
	\end{newitemize}
	}

	\job
	{Tumblr}
	{Nov 2014 - Aug 2015}
	{Services Engineer}
	{New York, NY}
	{
	\begin{newitemize}
		\item Contributed to ongoing development of Colossus, a
	high-performance Scala micro-services
	framework.
		\item Created a proxy server designed to run in Amazon EC2 cloud
		services which reduced S3 transfers and lowered monthly transfer
		costs by one sixth.
		\item Developed a solution for real-time updates using the
		Tumblr firehose, generating over 1 million Redis increments a
		second.
	\end{newitemize}
	}

	\job
	{Placeable}
	{Oct 2013 - Nov 2014}
	{Scala Developer}
	{Denver, CO}
	{
	\begin{newitemize}
		\item Created a system for generic data manipulation and export
in a Play 2.2 based service, with distribution to services such
as Google, Yelp, and Factual.
		\item Developed and implemented a migration path from multiple
Play instances to a clustered Akka actor system, using Mongo
capped collections as an event bus.
		\item Wrote documentation of API for internal and external use
in preparation for enabling third-party applications.
	\end{newitemize}
	}

	\job
	{ClickFox}
	{Aug 2011 - Aug 2013}
	{Software Engineer}
	{Denver, CO}
	{
	\begin{newitemize}
		\item Developed and maintained industry-leading cross-channel business analysis tools in Java using distributed GreenPlum databases and GridGain compute grids.
		\item Drove adoption of modern tools and practices, including
best practices of Mercurial source control and Maven build tool,
and integration of Jenkins build server with Redmine issue
tracking.
		\item Championed usage of agile methodologies; intrudoced a
two-week sprint and test driven development.
	\end{newitemize}
	}

	\job
	{Innoprise Software}
	{Aug 2010- May 2011}
	{Java Engineer}
	{Broomfield CO}
	{
	\begin{newitemize}
		\item Lead developer on a time-card entry system presented in
the Eclipse Rich Application Platform, hosted using GlassFish
OSGI, to integrate with the Innoprise enterprise resource
planning tools.
	\end{newitemize}
	}

	\job
	{Regis Learning Solutions, Inc (now The Regis Company)}
	{Mar 2009 - Aug 2011}
	{Lead Software Quality Assurance / Software Developer}
	{Golden CO}
	{
	\begin{newitemize}
		\item Developed and implemented test plans for e-learning
software. Testing involved creating test scripts on GUI
intensive applications, and exploratory testing in identified
problem areas.
 		\item Added Section 508 Accessibility compliance to a SCORM
framework in ActionScript 3.
		\item Created tools to quickly visualize XML configuration files
using Java 6.
	\end{newitemize}
	}
}
% Chapter: Skills
% ------------------------

\chap{SKILLS}{
	\begin{newitemize}
		\item Full Stack Development including architecture and infrastructure design
		\item Agile Software Development methodology including organizational design
		\item Talent development and performance coaching of individual contributors and managers
	
	\end{newitemize}
}
% Chapter: Projects
% ------------------------

% Chapter: Education
% ------------------

\chap{EDUCATION}{

\school
{Metropolitan State University of Denver}
{2006 – 2010}
{BS Computer Science}
{Denver}
{
}
}

\chap{ORGANIZATIONS AND PUBLIC APPEARANCES}{
	
	\project
	{Write/Speak/Code}
	{Treasurer}
	{2020-2022}
	{Write/Speak/Code was an 501c(3) organization dedicated to elevating women and non-binary people in thought leadership. As Treasurer, I had responsibility for ensuring the organization was compliant with all
	 applicable laws and had the finances available to accomplish its goals. As a general member of the board I set the direction of the organization.
	}
	
	\project
	{Write/Speak/Code}
	{Conference Content Chair}
	{2019}
	{The Write/Speak/Code conference was an annual event drawing up to 1500 attendees. The 2019 conference was held in San Francisco. As the Conference Content Chair, I was responsible for the Call for Proposals process,
	chaired the content selection committee, and coordinated with speakers and event staff to ensure the smooth operation of content.}
	
	\project
	{Global Diversity CFP Day}
	{Workshop Organizer, Presenter}
	{2018, 2019, 2020}
	{Global Diversity CFP Day is an international event of workshops designed to help attendees submit their first conference talk proposal. I was an organizer and presenter of the New York City event three years running. I created 
	and delivered a full day curriculum, coordinated individual coaches, and assisted in sponsorship, venue, and vendor activities.}
	
	\project
	{Write/Speak/Code}
	{New York Chapter Meetup Organizer}
	{2016-2020}
	{The Write/Speak/Code New York Chapter was the local chapter of the national Write/Speak/Code organization. We held monthly talks and workshops in the New York area. As an organizer, I sourced speakers, venues, and sponsors.}
	 
	\project
	{Codebar.io}
	{Coach}
	{2015-2018}
	{Codebar is an international organization offering coaching and mentorship to people learning to program. As a coach, I worked one-on-one or in small groups, helping learners with their own projects.}
	
	\project
	{Public Appearances}
	{}
	{}
	{\begin{newitemize}
		\item Write/Speak/Code Conference - 2019
		\item Women Who Code Connect- Mono and Micro, Mar 2018
		\item Global Diversity CFP Day - Workshop Facilitator, 2018,2019,2020
		\item Spring One Conference - Solid In The Wild, Dec 2017
		\item Write/Speak/Code - Workshop facilitator, Nov 2017
		\item Pivotal Tech Talk Tuesdays - Introduction to Reactive Streams, Jun 2017
		\item Write/Speak/Code - Product Killers, Dec 2016
		\item She Says Horror Stories 2 - Panelist, Oct 2016
		\item CODE Debugging the Gender Gap Screening - Panelist, May 2016
	\end{newitemize}
	}
	
	\project
	{Text Media}
	{}
	{}
	{\begin{newitemize}
		\item Being Your Authentic Self - Interview, Built To Adapt
\item Asking for Gender in Applications - Article, Built To Adapt	\end{newitemize}
	}
}
	
	\ 
\end{document}